\section{Open Problems}
Many problems on the algorithmic complexity of $\trsk$ remain 
open. The most impressive upper bound on query complexity would be the following.
\begin{open} \label{tarskiInP}
  Is the query complexity of $\trsk(N, d)$ $O(\poly(\log N) \cdot \poly(d))$?
\end{open}
The implications of a result in the positive for \cref{tarskiInP} would be significant to say the least.
For example, it would give a polynomial time algorithm for
computing the exact value of simple stochastic games as described in \cref{ssgs},
which has remained an open problem since 1992 when studied by Condon in \citep{condon}.
It would also imply a polynomial-time algorithm for the $\arr$ problem as described in \cref{arr},
the complexity of which has seen a significant amount of study in recent years
\citep{gärtner2021subexponential, gärtner2018arrival, arrivalBasic, arrLowerBound}.
Another implication would be a polynomial time algorithm for approximating the value of
stochastic games as in \cref{shapleyChap}. The strength of the implications of \cref{tarskiInP}
are evidence that solving it in the near future is unlikely, and that considering weaker conjectures
might be more realistic.
\begin{open} \label{tarskiFixedParameterTractable}
  Is the query complexity of 
  $\trsk(N, d)$ $O(\log^2 N)$ for fixed $d$? That is, is $\trsk$ fixed-parameter tractable?
\end{open}
Recent results such as \cref{tightThreeDimension} from \citep{fasterTarski} make this seem
plausible. Perhaps the notion of a 'witness' as described in \cref{witnessDef} can be
generalized to higher dimensions, with a method of halfing the search space as in \cref{innerMainCase}
in a potentially exponential number of queries? A useful intermediate result towards this problem could be
the following.
\begin{open} \label{tightFourDimension}
  Is the query complexity of $\trsk(N, 4)$ $O(\log^2 N)$?
\end{open}
Improved lower bounds for the $\trsk$ problem would also be an interesting
result. The most basic improvement could be something like the following.
\begin{open}
  For some $d \in \Z_{> 2}$ is the query complexity of
  $\trsk(N, d)$ $\omega(\log^2 N)$?
\end{open}
