\section{Further Work}
The main shortcoming of the testing I have carried out is the random instance generation described in \cref{randomGen}.
In all problems, the results such as \cref{arrivalWalkPlot} give strong evidence
that for the most basic algorithms like simulating the walk and value iteration,
my scheme for random problem generation does not generate 'hard' problems so investigation
into this could be carried out. Another extension
could be to implement strategy improvement and quadratic programming
to solve simple stochastic games and further compare.\\
In \citep{valueIterationTest} both of these issues are somewhat addressed when testing value iteration,
strategy improvement, and quadratic programming on simple stochatic games. The authors
build a library of extremal problems that are difficult for particular algorithms, as well as a more
sophisticated method of generating random problems than I have done here. Perhaps transitive
comparisons can be made to results in \citep{valueIterationTest} given
we have both tested value iteration, although the difference in how we generate problems makes this tenuous. \\
Time could be spent on on optimizing the monotone function for shapley's stochastic games,
as tests have been limited to small sizes so an increase in performance could yield more interesting data. \\
The asymptotic advantage the binary-search style algorithms achieve over the iterative algorithms
is dependent on the ratio between the height of the lattice and it's dimension. In particular
the asymptotic bound for FPS is stronger than KT if $d \in o(\frac{\log N}{\log \log N})$.
In simple and shapley's stochastic games, solving to higher precision $\varepsilon$ causes
an increase in the height of the searched lattice so testing with very high precision
approximation constraints along with finding 'hard' instances of these problems could
demonstrate a practical advantage to FPS over value iteration. This would require additional support
in my implementation for high precision numerical types such as GMP\citep{gmp}, and
I believe finding an LP solver for shapley's stochastic games 
with strong support for high precision types will also be difficult.
%todo note on strategy improvement
